---
title: "Max SPRT-I-AA All Steps for A/B Experiment"
author: "Emin Mansur Cengay"

output:
  html_document: default
  
---

# Data Creation

Create A/B data for the case p1 =0.5 and p2 =0.55

```{r}
  source("_1_Create_AB_Data.R")
  NumSim= 10

  library("parallel")
  p1=0.5
  p2=0.55
  print (round (power.prop.test(p1=p1, p2=p2, power=0.8)$n,0))

  NumIte10= round (power.prop.test(p1=p1, p2=p2, power=0.8)$n,0)

  y10  = mclapply(1:NumSim, f_create_1AB_data_faster  ,NumIte=NumIte10   ,p1=p1 ,p2=p2  , mc.cores = 10)
  x10  = do.call(rbind.data.frame, y10)
  names (x10) = c("numSim","numIte","Arm1_suc","Arm2_suc","Arm1_cum_suc","Arm2_cum_suc")


```




Create A/A data for the case p1 =0.5 and p2 =0.5 the length is equal to case p1=0.5 and p2=0.51

```{r}

  p1=0.5
  p2=0.51 # to calculate length
  print (round (power.prop.test(p1=p1, p2=p2, power=0.8)$n,0))

  NumIte0= round (power.prop.test(p1=p1, p2=p2, power=0.8)$n,0)
  y0  = mclapply(1:NumSim, f_create_1AB_data_faster  ,NumIte=NumIte0   ,p1=p1 ,p2=p1  , mc.cores = 10)
  x0  = do.call(rbind.data.frame, y0)
  names (x0) = c("numSim","numIte","Arm1_suc","Arm2_suc","Arm1_cum_suc","Arm2_cum_suc")

```

# Learning Upper Boundary

Calculate all LLR values with upper boundary algorithm on A/A data, we will slice it later.
```{r}
    source("_2_Learn_AA_Upper_Boundary.R")

    yAA  = mclapply(1:NumSim, AA_LLR_AB_AllSimulation_vector , DF_= x0 ,N =NumIte0 , mc.cores = 10)
    xAA   = do.call(rbind.data.frame, yAA)
    names (xAA) = 1:length(xAA)
```



Slice it for the corresponding length of the case. Batch size to stop will be different. We get the max  %95 because the  alpha value is 0.05

```{r}
    df = xAA
    batch0 = length ( seq(100,NumIte0, 100))  
    df[, "max"] <- apply(df[, 2:batch0], 1, max)
    sorted= sort(df$max, decreasing = FALSE)
    q0 =round(quantile (sorted,0.95),2)
    print ( paste0("Boundary for A/A: ",q0)) 
    
  
```

```{r}
     df = xAA
    batch10 = length ( seq(100,NumIte10, 100))  
    df[, "max"] <- apply(df[, 2:batch10], 1, max)
    sorted= sort(df$max, decreasing = FALSE)
    q10 =round(quantile (sorted,0.95),2)
    
    print ( paste0("Boundary for A/B: ",q10)) 
```

# Calculate LLR

Calculate the LLR for both A/A and A/B . Plot the average LLR valuse with boundries.
```{r}
  source ("_3_Calculate_LLR.R")
  ## on A/B data  
  y10_LLR  = mclapply(1:NumSim, maxSPRT_MAB_MC , DF_=x10 ,N =NumIte10 , mc.cores = 10)
  x10_LLR = do.call(rbind.data.frame, y10_LLR)
  
  ## on A/A  
  y0_LLR  = mclapply(1:NumSim, maxSPRT_MAB_MC , DF_=x0 ,N =NumIte0 , mc.cores = 10)
  x0_LLR = do.call(rbind.data.frame, y0_LLR)
  
   # plot avg LLR with boundary
  p1         = 0.5
  r          = c(0,10)
  plot (colMeans (x10_LLR)   ,  type = "l", col="blue", lwd =2, ylab = "LLR" , xlab = "Number of Batch" , main = paste0("Max SPRT-I-AA: A/B LLR & Boundary\n p1= ",p1," vs Delta")     ,ylim = c(0,5))
  lines(colMeans (x0_LLR)    , col="red"   , lwd=4 )
  abline(h=q10 , col="blue"  , lwd=2, lty=2 )
  abline(h=q0  , col="red"   , lwd=2, lty=4 )
  grid (NULL,NULL, lty = 6, col = "cornsilk2") 
  legend("bottomright",legend=c("10","0"), col=c("blue","red"),lty = 1, ncol=1)
```


# Making a Decision 

 Make decision, stop the experiment if LLR cross the upper boundary. If LLR do not cross the boundary during the experimen accept H0.
 
```{r}
  source ("_4_Make_Decision.R")
  
  
  y10_Decision  = mclapply(1:NumSim, AB_Boundries_1row , DF_= x10_LLR  ,threshold= q10, mc.cores = 10)
  x10_Decision = do.call(rbind.data.frame, y10_Decision)
  print ("Type 2 error rate")
  print (table (x10_Decision$Decision))
  
  
  y0_Decision  = mclapply(1:NumSim, AB_Boundries_1row , DF_= x0_LLR  ,threshold= q0, mc.cores = 10)
  x0_Decision = do.call(rbind.data.frame, y0_Decision)
  print ("Type 1 error rate")
  print (table (x0_Decision$Decision))
```




## How quickly H1 is accepted. How much time is saved

```{r}

  resultH1 = subset(x10_Decision, Decision=="AcceptH1")
  
  nmean =round (mean(resultH1$i),0)
  RequiredBatch = NumIte10/100
  saved = (RequiredBatch-nmean)/RequiredBatch  
  
  print (round (saved,2))
  
  
  hist(resultH1$i,  main = paste0("Early Stopping") , xlab = "Number of Batch" , col="bisque" ,xlim=c(0,RequiredBatch))
  grid()
  abline(v=RequiredBatch, col="red", lwd=2)
  abline(v=nmean, col="blue", lwd=2)
  
  
  legend(x = "topright", inset=.05, 
         c( paste0(RequiredBatch), paste0(nmean)),
         col = c("red", "blue"),
         lwd = c(1, 1),
         cex=1,
         title="Calculated - Average Batch "
  )
  
  
```


## When H0 accepted

H0 is accepted, when the LLR do not cross the boundary during the experiment so it is accepted at the end of the experiment. The batch size was 100 so it fits.

```{r}

  resultH0 = subset(x0_Decision, Decision=="AcceptH0")
  
  # distinct values on H0 accepted batch
  unique (resultH0$i)
  
  # experiment length
  NumIte0
  
  

```

